---
title: "Untitled"
author: "Joshua Ashkinaze"
date: "2023-08-10"
output: html_document
---

```{r packages}
library(purrr)
library(dplyr)
library(ggplot2)
library(glmmTMB)
library(lmtest)
library(sandwich)
library(stargazer)
library(lmtest)
library(gtsummary)
library(broom.mixed)
library(jtools)
library(ggthemes)
library(checkmate)
library(blme) 
library(vtable)
library(DescTools)
library(marginaleffects)
library(sandwich)
library(lmtest)
nt <- min(parallel::detectCores(),20)
```

```{r read-data}

process_data <- function(cur_ideology) {

  file_name <- paste0("processed/s2_mar23_oct23_ideo", cur_ideology, "_final_mod")
  nt <- min(parallel::detectCores(), 20)

  min_zero <- function(input_vector) {
    output_vector <- ifelse(input_vector > 0, input_vector, 0)
    return(output_vector)
  }

  if (!file.exists(paste0(file_name, ".rds"))) {
    df2 <- read.csv(paste0(file_name, ".csv"))
    df2$main <- as.factor(df2$main)
    df2$is_liberal <- (df2$theta < 0) * 1
    df2$followers_id <- as.factor(df2$followers_id)
    df2$tie_id <- as.factor(paste0(df2$followers_id, df2$main, sep="_"))
    df2$abs_ideo <- abs(df2$theta)
    df2$spreader_follow_prop <- (df2$n_spreader_following / pmax(df2$follower_following_count, 1))
    df2$n_spreader_following_prop <- (df2$n_spreader_following / pmax(df2$follower_following_count, 1))
    saveRDS(df2, paste0(file_name, ".rds"), compress = FALSE)
  } else {
    df2 <- readRDS(paste0(file_name, ".rds"))
  }

  return(df2)
}

df2 <- process_data("Y")


```

# Run Models and Marginal Effects

```{r run-models}


 clear_environment <- function(df) {
  # Creates a new data frame without the original environment
  as.data.frame(unclass(df))
  }


compute_marginal_fx <-

  function(model,
           run_type,
           model_name,
           data_set,
           ideology) {
    marginal_list <- list()
    
    fn <-
      paste0(paste0(run_type, model_name, data_set, ideology, sep = "_"),
             "marginal.rds")
    
    marginal_list[['liberal_comparison']] <-
      avg_comparisons(model,
                      by = "is_liberal",
                      comparison = "lnoravg",
                      transform = "exp")  %>% as.data.frame(.) %>% tibble(.)
    
    marginal_list[['overall_comparison']] <-
      avg_comparisons(model)  %>% as.data.frame(.) %>% tibble(.)
    
    marginal_list[['liberal_interactions']] <-
      avg_comparisons(
        model,
        comparison = "lnoravg",
        transform = "exp",
        variables = c("abs_ideo", "n_spreader_following"),
        by = "is_liberal",
      ) %>% as.data.frame(.) %>% tibble(.)
    
    marginal_list[['liberal_interactions_p']] <-
      avg_comparisons(
        model,
        comparison = "lnoravg",
        transform = "exp",
        hypothesis = "pairwise",
        variables = c("abs_ideo", "n_spreader_following"),
        by = "is_liberal"
      ) %>% as.data.frame(.) %>% tibble(.)
    
    
    
    marginal_list[['overall_interactions']] <-
      slopes(
        model,
        variables = "abs_ideo",
        newdata = datagrid(n_spreader_following = c(-2,-1, 0, 1, 2)),
        type = 'response'
      ) %>% as.data.frame(.) %>% tibble(.)
    
    
    marginal_list[['overall_interactions_p']] <-
      slopes(
        model,
        variables = "abs_ideo",
        newdata = datagrid(n_spreader_following = c(-2,-1, 0, 1, 2)),
        type = 'response',
        hypothesis = "pairwise"
      ) %>% as.data.frame(.) %>% tibble(.)
    
    # Apparently R links the large model object as a refernece
    # to derived content, such as dataframes 
    marginal_list <- lapply(marginal_list, clear_environment)
    saveRDS(marginal_list, fn)
    return(marginal_list)
  }


standardize_preds <- function(data, columns) {
  data <- data %>%
    mutate(across(all_of(columns), ~ ((. - mean(
      .
    )) / sd(.))))
  return(data)
}

standardize_preds_gelman <- function(data, columns) {
  data <- data %>%
    mutate(across(all_of(columns), ~ ((. - mean(
      .
    )) / (2 * sd(
      .
    )))))
  return(data)
}

center_binary_variable_gelman <- function(binary_variable) {
  p <- mean(binary_variable)
  centered_variable <- ifelse(binary_variable == 1, 1 - p, -p)
  return(centered_variable)
}

run_model <-
  function(method,
           data_set,
           rfx_opt,
           run_mode,
           ideology) {
    
    # Define predictor variables
    if (data_set == 'minimal') {
      if (ideology == "Y") {
        numeric_ivs <-
          c(
            "follower_tweet_count",
            "follower_following_count",
            "follower_follower_count",
            "spreader_tweet_count",
            "spreader_following_count",
            "spreader_follower_count",
            "n_spreader_following",
            "change_spreader_tweet_count2",
            "abs_ideo"
          )
      } else{
        numeric_ivs <-
          c(
            "follower_tweet_count",
            "follower_following_count",
            "follower_follower_count",
            "spreader_tweet_count",
            "spreader_following_count",
            "spreader_follower_count",
            "n_spreader_following",
            "change_spreader_tweet_count2"
          )
      }
      
      
    } else if (data_set == 'maximal') {
      numeric_ivs <-
        c(
          "follower_tweet_count",
          "follower_following_count",
          "follower_follower_count",
          "change_follower_tweet_count2",
          "change_follower_following_count2",
          "change_follower_follower_count2",
          "spreader_tweet_count",
          "spreader_following_count",
          "spreader_follower_count",
          "change_spreader_tweet_count2",
          "change_spreader_following_count2",
          "change_spreader_follower_count2",
          "n_spreader_following",
          "abs_ideo"
        )
    }
    
    if (ideology == "Y") {
      binary_ivs <- c('recip', 'is_liberal')
    } else {
      binary_ivs <- c('recip')
    }
    
    
    if (ideology == "Y") {
      all_ivs <-
        c(
          binary_ivs,
          numeric_ivs,
          c(
            "abs_ideo*is_liberal",
            "is_liberal*n_spreader_following",
            "n_spreader_following*abs_ideo"
          )
        )
    } else{
      all_ivs <-
        c(binary_ivs,
          numeric_ivs)
    }
    
    # Define the formula string
    formula_str <-
      paste("unfollowed ~", paste(all_ivs, collapse = " + "))
    
    
    # Rescale predictors
    df3 <- process_data(ideology)
    
    if (run_mode == 'debug') {
      df3 <- df3 %>% group_by(unfollowed) %>% sample_n(1000) %>% ungroup()
    }
    
    df3 <- standardize_preds(df3, numeric_ivs)
    
    if (method == 'simple') {
      fit <- glm(formula_str, data = df3, family = 'binomial')
      print(summary(fit))
      if (ideology == "Y") {
        compute_marginal_fx(fit, run_mode, "simple", data_set, ideology)
      }
      saveRDS(fit, paste0(data_set, run_mode, ideology, "_simple.rds"))
      
    } else if (method == 'bayesian') {
      # Add random effects part to the formula for Bayesian and lmer
      if (rfx_opt == 'simple') {
        formula_str <- paste(formula_str, "+ (1|main)")
      }
      else {
        formula_str <- paste(formula_str, "+ (1|main/tie_id)")
      }
      
      bayes_fit <-
        bglmer(
          as.formula(formula_str),
          data = df3,
          family = "binomial",
          verbose = 2L,
          control = glmerControl(
            optimizer = "nlminbwrap",
            optCtrl = list(maxfun = 5000)
          ),
          fixef.prior = t(df = 7, scale = 2.5)
        )
      print(summary(bayes_fit))
      print("Summarized bayes")
       if (ideology == "Y") {
         compute_marginal_fx(bayes_fit,
                             run_mode,
                             "bayes",
                             data_set,
                             ideology)
         print("Got marginal fx for bayes")
      }
      saveRDS(bayes_fit,
              paste0(
                run_mode,
                data_set,
                rfx_opt,
                ideology,
                paste0("_bayes_rfx.rds")
              ))
      print("Saved bayes")
  
      }
  }



# NOTE: Simplified to only have random intercept for spreaders

run <- "debug" # either 'real' or 'debug'
ideology_sample <-
  c("Y", "N") # whether to include ideology or not -- Y or N
methods <-
  c("bayesian", "simple") # simple, bayesian, lmer, glmm --> Only use bayesian and simple for paper
data_sets <-
  c("minimal") # minimal, maximal --> Only use minimal for paper
rfx_opt <-
  c('simple') # simple, nested --> only use "simple" for paper
model_results <- list()

for (cur_ideology in ideology_sample) {
  process_data(cur_ideology)
  for (data_set in data_sets) {
    for (method in methods) {
      for (ropt in rfx_opt) {
          run_model(
            method = method,
            data_set = data_set,
            rfx_opt = ropt,
            run_mode = run,
            ideology = cur_ideology
          )
      }
    }
  }
}
  

saveRDS(model_results,
        paste0("model_results", run, cur_ideology, ".rds"))
```

# Get Marginal Effects Only 

```{r margins-only}

clear_environment <- function(df) {
    # Creates a new data frame without the original environment
    as.data.frame(unclass(df))
  }
  

compute_marginal_fx <-
  function(model,
           run_type,
           model_name,
           data_set,
           ideology) {
    marginal_list <- list()
    
    
    fn <-
      paste0(paste0(run_type, model_name, data_set, ideology, sep = "_"),
             "marginal.rds")
    
    marginal_list[['liberal_comparison']] <-
      avg_slopes(model,
                      by = "is_liberal")  %>% as.data.frame(.) %>% tibble(.)
    
    marginal_list[['overall_comparison']] <-
      avg_slopes(model)  %>% as.data.frame(.) %>% tibble(.)
    
    marginal_list[['liberal_interactions']] <-
      avg_slopes(
        model,
        variables = c("abs_ideo", "n_spreader_following"),
        by = "is_liberal",
      ) %>% as.data.frame(.) %>% tibble(.)
    
    marginal_list[['liberal_interactions_p']] <-
      avg_slopes(
        model,
        hypothesis = "pairwise",
        variables = c("abs_ideo", "n_spreader_following"),
        by = "is_liberal"
      ) %>% as.data.frame(.) %>% tibble(.)
    
    
    marginal_list[['overall_interactions']] <-
      slopes(
        model,
        variables = "n_spreader_following",
        newdata = datagrid(abs_ideo = c(-2,-1, 0, 1, 2)),
        type = 'response'
      ) %>% as.data.frame(.) %>% tibble(.)
    
    
    marginal_list[['overall_interactions_p']] <-
      slopes(
        model,
        variables = "n_spreader_following",
        newdata = datagrid(abs_ideo = c(-2,-1, 0, 1, 2)),
        type = 'response',
        hypothesis = "pairwise"
      ) %>% as.data.frame(.) %>% tibble(.)
    
    
    marginal_list <- lapply(marginal_list, clear_environment)
    saveRDS(marginal_list, fn)
    return(marginal_list)
    
    
  }

bayes.model <- readRDS("realminimalsimpleY_bayes_rfx.rds")
simple.model <- readRDS("minimalrealY_simple.rds")
simple_marginal <- compute_marginal_fx(simple.model,"real2", "simple", "minimal", "Y")

```

# Marginal Plots

## Ideology Model

```{r margin-graphs}
library(ggthemes)
library(dplyr)
library(ggplot2)

library(dplyr)
library(ggplot2)

clean_labels <- function(labels) {
  sapply(labels, function(label) {
    if (startsWith(label, "n_")) {
      label <- paste0("N ", substr(label, 3, nchar(label)))
    }
    label <- gsub("_", " ", label)
    label <- gsub("[0-9]", "", label)
    label <- tools::toTitleCase(label)
    return(label)
  })
}

print_AME_CI <- function(df) {
  cat("\nAverage Marginal Effects and 95% Confidence Intervals:\n")
   
  for(i in 1:nrow(df)) {
    variable_name <- df[i, "term"]
    estimate <- df[i, "estimate"]
    lower_bound <- df[i, "conf.low"]
    upper_bound <- df[i, "conf.high"]
    
    cat(sprintf("%s: (AME = %.4f, 95%% CI = [%.4f, %.4f])\n",
                variable_name, estimate, lower_bound, upper_bound))
  }
}


margins <- readRDS("real2simpleminimalY_marginal.rds")


# overall fx 
print_AME_CI(margins$overall_comparison)

# interactions -- first is conservative then liberals
print_AME_CI(margins$liberal_comparison)

graph.overall <-
  margins$overall_comparison %>%
  as.data.frame() %>%
  mutate(term2 = clean_labels(term)) %>%
  ggplot(aes(x = estimate, y = reorder(term2, estimate))) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.4) +
  theme_minimal(base_size = 15) +
  geom_point(size = 2) +
  theme(
     panel.grid.minor.y = element_blank(
      
    ),
    panel.grid.major.y = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.major.x = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.minor.x = element_blank(
    ), plot.title = element_text(face = "bold"),
      axis.title.x = element_text(vjust = -1.2)  # Adjust this value to move the x-axis label

  ) +
  geom_vline(
    xintercept = 0,
    linetype = 'dashed',
    size = 1,
    color = 'red'
  ) +
  labs(
    title = "Average Marginal Effects of Unfollowing",
    subtitle = "Average marginal effects (no interactions) and 95% CIs of a +1\nSD change on probability of unfollowing",
    x = "Marginal Effect\n(Probability Scale)",
    y = "Coefficient"
  )
ggsave(
  "graph_overall.png",
  graph.overall,
  height = 5,
  width = 9,
  dpi = 300
) 


graph.inter.entrench.prez <-
  margins$liberal_comparison %>% as.data.frame() %>%
  filter(term %in% c("n_spreader_following")) %>%
  mutate(lib = ifelse(is_liberal == 1, "Liberal", "Conservative")) %>%
  ggplot(data = ., aes(x = lib, y = estimate)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  theme_nice() + # Commented out since it's not standard ggplot2
  geom_point(size = 2) +
  geom_line(
    aes(group = 1),
    size = 1,
    linetype = 'solid',
    color = 'black'
  ) + 
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA)
  ) +
  labs(
    title = "Effect of T1 exposure on probability unfollowing, by political ideology",
    y = "Marginal Effect\n(Probability Scale)",
    x = "Ideology",
    subtitle = "Group level AME (95% CI) of a +1 SD increase in number of spreaders followed at T1\non probability of unfollowing a spreader at T2"
  ) +
  geom_line(
    aes(group = 1),
    size = 1,
    linetype = 'solid',
    color = 'black'
  )
ggsave("graph.inter.entrench.prez.png", graph.inter.entrench.prez, dpi=300, width=9, height=5, bg="transparent")



graph.inter.entrench.paper <- margins$liberal_comparison %>% as.data.frame() %>% 
  filter(term %in% c("n_spreader_following")) %>% 
   mutate(lib = ifelse(is_liberal == 1, "Liberal", "Conservative")) %>% 
  ggplot(data=., aes(x=lib, y=estimate)) + 
  geom_point(size=5) + 
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width=0.3) +  
  theme_minimal(base_size = 20) +
  geom_point(size = 2) +
  theme(
     panel.grid.minor.y = element_blank(
      
    ),
    panel.grid.major.y = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.major.x = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.minor.x = element_blank(
    ), plot.title = element_text(face = "bold"),
     axis.title.x = element_text(vjust = -1.2) 
  ) +
  labs(title="How T1 exposure affects probability of\nunfollowing (by partisan alignment)", y="Marginal Effect\n(Probability Scale)", x="Ideology", subtitle="AME (95% CI) of a +1 SD increase in T1 exposure") + 
  geom_line(aes(group=1), size=1, linetype='solid', color='black') 
ggsave("graph.inter.entrench.paper.png", graph.inter.entrench.paper, dpi=400, width=9, height=5)


graph.inter.ideo.prez <- margins$liberal_comparison %>% 
  as.data.frame() %>% 
  filter(term %in% c("abs_ideo")) %>% 
  mutate(lib = ifelse(is_liberal == 1, "Liberal", "Conservative")) %>% 
  ggplot(data=., aes(x=lib, y=estimate)) + 
  geom_point(size=5) + 
  theme_nice() +  
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width=0.3) +  # Reduce width here
  labs(title="How ideological strength affects probability of unfollowing a misinformation\nspreader (by partisan alignment)", y="Marginal Effect\n(Probability Scale)", x="Ideology", subtitle="AME (95% CI) of a +1 SD increase in absolute value of ideology on probability of\nunfollowing a spreader at T2") + 
  geom_line(aes(group=1), size=1, linetype='solid', color='black') + geom_hline(yintercept=0, linetype='dashed', size=2, color='red') + 
  theme(panel.background = element_rect(fill = "transparent", colour = NA),  plot.background = element_rect(fill = "transparent", colour = NA))
ggsave("graph.inter.ideo.prez.png", graph.inter.ideo.prez, dpi=300, width=9, height=5, bg="transparent")

graph.inter.ideo.paper <- margins$liberal_comparison %>% 
  as.data.frame() %>% 
  filter(term %in% c("abs_ideo")) %>% 
  mutate(lib = ifelse(is_liberal == 1, "Liberal", "Conservative")) %>% 
  ggplot(data=., aes(x=lib, y=estimate)) + 
  geom_point(size=6) + 
  theme_minimal(base_size = 20) +
  theme(
     panel.grid.minor.y = element_blank(
      
    ),
    panel.grid.major.y = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.major.x = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.minor.x = element_blank(
    ), plot.title = element_text(face = "bold"),
     axis.title.x = element_text(vjust = -1.2) 
  ) +

  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width=0.3) +  # Reduce width here
  labs(title="How ideological strength affects probability\nof unfollowing (by partisan alignment)", y="Marginal Effect\n(Probability Scale)", x="Ideology", subtitle="AME (95% CI) of a +1 SD increase in ideological strength") + 
  geom_line(aes(group=1), size=1, linetype='solid', color='black') + geom_hline(yintercept=0, linetype='dashed', size=2, color='red') 
ggsave("graph.inter.ideo.paper.png", graph.inter.ideo.paper, dpi=400, width=9, height=5, bg="transparent")


graph.entrench_abs <- margins$overall_interactions %>% 
  as.data.frame() %>% 
  dplyr::mutate(abs_ideo = case_when(
    abs_ideo == -2 ~ "-2 SD",
    abs_ideo == -1 ~ "-1 SD",
    abs_ideo ==  0 ~ "Mean",
    abs_ideo ==  1 ~ "+1 SD",
    abs_ideo ==  2 ~ "+2 SD"  # This line ensures that any value not specified above remains as it is.
  )) %>% 
  ggplot(data=., aes(x=reorder(abs_ideo, -1*estimate), y=estimate)) + 
  geom_point(size=6) + 
  theme_nice() +  
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width=0.3) +  # Reduce width here
  labs(title="How ideological strength moderates the effect of T1 exposure on the probability of\nunfollowing a misinformation spreader", y="Marginal Effect\n(Probability Scale)", x="Absolute Value Ideology", subtitle="AME (95% CI) of a +1 SD increase in T1 exposure on probability of\nunfollowing a spreader at T2") + 
  geom_line(aes(group=1), size=1, linetype='solid', color='black') + geom_hline(yintercept=0, linetype='dashed', size=2, color='red') + 
  theme(panel.background = element_rect(fill = "transparent", colour = NA),  plot.background = element_rect(fill = "transparent", colour = NA))
ggsave("graph.entrench_abs.png", graph.entrench_abs, dpi=300, width=9, height=5, bg="transparent")
  
  


graph.entrench_abs.paper <- margins$overall_interactions %>% 
  as.data.frame() %>% 
  dplyr::mutate(abs_ideo = case_when(
    abs_ideo == -2 ~ "-2 SD",
    abs_ideo == -1 ~ "-1 SD",
    abs_ideo ==  0 ~ "Mean",
    abs_ideo ==  1 ~ "+1 SD",
    abs_ideo ==  2 ~ "+2 SD"  # This line ensures that any value not specified above remains as it is.
  )) %>% 
  ggplot(data=., aes(x=reorder(abs_ideo, estimate), y=estimate)) + 
  geom_point(size=6) + 
    theme_minimal(base_size = 20) +
  theme(
     panel.grid.minor.y = element_blank(
      
    ),
    panel.grid.major.y = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.major.x = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.minor.x = element_blank(
    ), plot.title = element_text(face = "bold"),
     axis.title.x = element_text(vjust = -1.2) 
  ) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), width=0.3) +  # Reduce width here
  labs(title="How ideological strength moderates the\neffect of T1 exposure on the probability\nof unfollowing", y="Marginal Effect\n(Probability Scale)", x="Ideological Strength\n(Absolute Value of Ideology)", subtitle="AME (95% CI) of a +1 SD increase in T1 exposure") + 
  geom_line(aes(group=1), size=1, linetype='solid', color='black') 
ggsave("graph.entrench_abs.paper.png", graph.entrench_abs.paper, dpi=400, width=9, height=5, bg="transparent")
  


```
# Logit Graphs (Raw)

```{r}
margins$liberal_comparison %>%
  as.data.frame() %>%
  clear_environment()
  filter(term %in% c("abs_ideo", "n_spreader_following")) %>%
  mutate(id = ifelse(is_liberal, "(Liberal)", "(Conservative)"))

```


# Robustness Checks - Different models

## Fit the non ideology model on the ideology = Y section. 

The idea is to make sure non ideology variables don't differ for folks whose 
ideology can be matched 

```{r}

if (!file.exists("no_id_model_for_idY3.rds")) {
  numeric_ivs <-
    c(
      "follower_tweet_count",
      "follower_following_count",
      "follower_follower_count",
      "spreader_tweet_count",
      "spreader_following_count",
      "spreader_follower_count",
      "n_spreader_following",
      "change_spreader_tweet_count2"
    )
  binary_ivs <- c('recip')
  all_ivs <-c(binary_ivs,numeric_ivs)
  formula_str <-paste("unfollowed ~", paste(all_ivs, collapse = " + "))
  dfY <- process_data("Y")
  dfY <- standardize_preds(dfY, numeric_ivs)
  fit <- glm(formula_str, data = dfY, family = 'binomial')
  saveRDS(fit, "no_id_model_for_idY.rds")
} else{
  #pass
}




```


## Main Specification 
### Read in models
```{r}
bayesian.Y <- readRDS("realminimalsimpleY_bayes_rfx.rds")
basic.Y <- readRDS("minimalrealY_simple.rds")
```

### Stargazer tables
```{r}
# NOTE: Following this guide for including bayesian mxed models in stargazer tables
# http://svmiller.com/blog/2020/05/better-way-to-include-random-effects-stargazer/

clean_labels <- function(labels) {
  sapply(labels, function(label) {
    if (startsWith(label, "n_")) {
      label <- paste0("N ", substr(label, 3, nchar(label)))
    }
    label <- gsub("_", " ", label)
    label <- gsub("[0-9]", "", label)
    label <- tools::toTitleCase(label)
    return(label)
  })
}

df3 <- readRDS("processed/s2_mar23_oct23_ideoY_final_mod.rds")
basic.Y.vcov <- vcovCL(basic.Y, cluster=~main)
basic.Y.coefs <- coeftest(basic.Y,  vcov = basic.Y.vcov, type="HC1")

basic.Y.tidy <- broom::tidy(basic.Y)
bayesian.Y.tidy <- broom::tidy(bayesian.Y) %>% filter(effect == "fixed")
sd_spreader <- round(as.numeric(attributes(VarCorr(bayesian.Y)$"main")$stddev), 3)

mod_stats <- tribble(~stat, ~basic.Y, ~bayesian.Y,
        "sd(spreader)", NA, sd_spreader,
        "", NA, NA,
        "N", nobs(basic.Y), nobs(bayesian.Y)) 

stargazer(basic.Y, basic.Y, 
          # ^ Call the first model twice so coefs are in stargazer, 
          # then replace estimates and SEs with the Bayesian ones 
          coef = list(basic.Y.tidy$estimate, bayesian.Y.tidy$estimate), #(normal, bayesian)
          se = list(basic.Y.coefs[,2], bayesian.Y.tidy$std.error), #(normal, bayesian)
          omit.table.layout = "s",
          add.lines = lapply(1:nrow(mod_stats), function(i) unlist(mod_stats[i, ])),
          model.names = FALSE,
          column.sep.width = "1pt", 
          single.row = TRUE,
          type='text',

          title = "Bayesian hierarchical logistic regressionvs non-hierarchical logistic regression with HC1 cluster robust errors at the spreader level. Note: Non-binary variables are z-scored so coefficients can be interpreted as the accompanying change in the log odds of unfollowing with a +1SD increase in the predictor variable.",
          column.labels = c("Cluster-Robust Logistic Regression", "Bayesian Multilevel Logistic Regression"), out='main_specification.tex')
  
```
### Plot Models 
```{r fig.width=10, fig.height=8}
library(sandwich)
library(lmtest)

clean_labels <- function(labels) {
  sapply(labels, function(label) {
    if (startsWith(label, "n_")) {
      label <- paste0("N ", substr(label, 3, nchar(label)))
    }
    label <- gsub("_", " ", label)
    label <- gsub("[0-9]", "", label)
    label <- tools::toTitleCase(label)
    return(label)
  })
}
# 

bayes.tidy <-  tidy(bayesian.Y) %>% 
  mutate(model = "Bayesian Multilevel") %>%
  filter(effect == "fixed") %>%
  select(term, estimate, std.error, p.value, model)%>% 
  cbind(confint(bayesian.Y, method='Wald') %>% na.omit())


simple.tidy <- tidy(basic.Y.coefs) %>% 
  cbind(coefci(basic.Y, vcov=basic.Y.vcov)) %>%
  mutate(model = "Cluster Robust") %>%
  select(term, estimate, std.error, p.value, model, `2.5 %`, `97.5 %`) 
 
both <- rbind(bayes.tidy, simple.tidy) %>%
  mutate(
    term2 = clean_labels(term),
  ) 


model.comparison.y <- ggplot(data=both, aes(x=estimate, y=reorder(term2, estimate), colour=model)) + 
  geom_point(size=3, position=position_dodge(width=0.5))  + 
  geom_errorbarh(aes(xmin=`2.5 %`, xmax=`97.5 %`), position=position_dodge(width=0.5)) + 
  labs(y="Term", x="Logit Coefficient", 
       title="Comparison of Models (Point Estimate and 95%CIs)", 
       subtitle="Bayesian hierarchical logistic regression vs non-hierarchical logistic regression with HC1 cluster\nrobust errors at the spreader level. Note: Non-binary coefficients are z-scored, so estimates can be\ninterpreted as an effect of a + 1SD increase on log odds of unfollowing.") + 
  theme_nice()
model.comparison.y
ggsave("model_comparisony.png", dpi=400)

```

## Non ideology
### Read in models
```{r}
# noid.N <- readRDS("minimalrealN_simple.rds")
# noid.Y <- readRDS("no_id_model_for_idY.rds")
# 
# 
df3 <- readRDS("processed/s2_mar23_aug23_ideoN_final_mod.rds")
noid.N.vcov <- vcovCL(noid.N, cluster=~main)
noid.N.coefs <- coeftest(noid.N ,  vcov = noid.N.vcov, type="HC1")

dfY <- readRDS("processed/s2_mar23_aug23_ideoY_final_mod.rds")
noid.Y.vcov <- vcovCL(noid.Y, cluster=~main)
noid.Y.coefs <- coeftest(noid.Y ,  vcov = noid.Y.vcov, type="HC1")
```


### Plot models
```{r fig.width=12, fig.height=8}
noid.N.tidy <- tidy(noid.N) %>% 
  cbind(coefci(noid.N, vcov=noid.N.vcov)) %>%
  mutate(Sample = "All Followers") %>%
  select(term, estimate, std.error, p.value, Sample, `2.5 %`, `97.5 %`) 

noid.Y.tidy <- tidy(noid.Y) %>% 
  cbind(coefci(noid.Y, vcov=noid.Y.vcov)) %>%
  mutate(Sample = "Matched Ideology") %>%
  select(term, estimate, std.error, p.value, Sample, `2.5 %`, `97.5 %`) 

comb <- rbind(noid.Y.tidy, noid.N.tidy) %>%  mutate(
    term2 = clean_labels(term))

model.comparison.n <- ggplot(data=comb, aes(x=estimate, y=reorder(term2, estimate), colour=Sample)) + 
  geom_point(size=8, position=position_dodge(width=0.5))  + 
  geom_errorbarh(aes(xmin=`2.5 %`, xmax=`97.5 %`), size=1, position=position_dodge(width=0.5)) + 
  labs(y="Term", x="Logit Coefficient") + 
  theme_classic(base_size = 25) + 
   scale_color_manual(
    values = c("All Followers" = "#EF476F", "Matched Ideology" = "#826AED")
  )
model.comparison.n
ggsave("model_comparison.png", dpi=400, height=8, width=16)

```


## Make plot

```{r fig.width=10, fig.height=8}
library(sandwich)
library(lmtest)

clean_labels <- function(labels) {
  sapply(labels, function(label) {
    if (startsWith(label, "n_")) {
      label <- paste0("N ", substr(label, 3, nchar(label)))
    }
    label <- gsub("_", " ", label)
    label <- gsub("[0-9]", "", label)
    label <- tools::toTitleCase(label)
    return(label)
  })
}
# 

bayes.tidy <-  tidy(bayesian.Y) %>% 
  mutate(model = "Bayesian Multilevel") %>%
  filter(effect == "fixed") %>%
  select(term, estimate, std.error, p.value, model)%>% 
  cbind(confint(bayesian.Y, method='Wald') %>% na.omit())


simple.tidy <- tidy(basic.Y.coefs) %>% 
  cbind(coefci(basic, vcov=basic.Y.vcov)) %>%
  mutate(model = "HC1 Cluster Robust Logit") %>%
  select(term, estimate, std.error, p.value, model, `2.5 %`, `97.5 %`) 
 
both <- rbind(bayes.tidy, simple.tidy) %>%
  mutate(
    term2 = clean_labels(term),
  ) %>%
  filter(term != "(Intercept)")

model.comparison.y <- ggplot(data=both, aes(x=estimate, y=reorder(term2, estimate), colour=model)) + 
  geom_point(size=3, position=position_dodge(width=0.5))  + 
  geom_errorbarh(aes(xmin=`2.5 %`, xmax=`97.5 %`), position=position_dodge(width=0.5)) + 
  labs(y="Term", x="Logit Coefficient", 
       title="Comparison of Models (Point Estimate and 95% Wald CIs)", 
       subtitle="Bayesian hierarchical logistic regression with t (7,2.5) priors vs non-hierarchical logistic regression with HC1 cluster\nrobust errors at the spreader level. Note: Non-binary coefficients are z-scored, so estimates can be interpreted as an\neffect of a + 1SD increase") + 
  theme_nice()
model.comparison.y
ggsave("model_comparisony.png", dpi=400)

```

```{r}
#-0.9892818009

# 0.9892818009
#-1.030675995

 tidy(bayesian) %>% 
  mutate(model = "Bayesian Multilevel") %>%
  filter(effect == "fixed") %>%
  select(term, estimate, std.error, p.value, model)%>% 
  cbind(confint(bayesian, method='Wald') %>% na.omit())
 

```

```{r}

samp <- df2 %>% group_by(unfollowed) %>% sample_n(10000)


```

```{r}
library(broom.mixed)
a <- glm("unfollowed ~ n_spreader_following*is_liberal + abs_ideo*is_liberal + abs_ideo*n_spreader_following", family='binomial', data=df2)
```

```{r}
bayesian <- readRDS("minimalrealY_bayes_rfx.rds")

```

```{r}
#1.608e-05
# -2.6e-07
df1 <- df2 %>% group_by(unfollowed) %>% sample_n(5000)

af <- allFit(bglmer(
            "unfollowed ~ n_spreader_following + (1|main)",
            data = df1,
            family = "binomial",
            verbose = 2L,
            fixef.prior = t(df = 7, scale = 2.5)
          ), maxfun=50000)

saveRDS(af, "all_fits.RDS")
```

```{r}
d <- df2 %>% dplyr::sample_n(2000)
d$abs_scaled <- scale(d$abs_ideo)
d$n_scaled <- scale(d$n_spreader_following)
l <- glm(unfollowed ~ abs_ideo + n_spreader_following, data=d)

   b <-
      slopes(
        l,
        variables = "n_spreader_following",
        newdata = datagrid(abs_ideo = c(-2,-1, 0, 1, 2)),
        type = 'response',
        hypothesis = "pairwise"
      ) %>% as.data.frame(.) %>% tibble(.)
```

```{r}
graph.overall <-
  margins$overall_comparison %>%
  as.data.frame() %>%
  mutate(term2 = clean_labels(term)) %>%
  ggplot(aes(x = estimate, y = reorder(term2, estimate))) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.4) +
  theme_minimal(base_size = 15) +
  geom_point(size = 2) +
  theme(
    panel.grid.major.y = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.major.x = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    panel.grid.minor.x = element_line(
      linewidth = 0.5,
      colour = 'lightgray',
      linetype = 'dashed'
    ),
    plot.title = element_text(face = "bold")
  ) +
  geom_vline(
    xintercept = 0,
    linetype = 'dashed',
    size = 1,
    color = 'red'
  ) +
  labs(
    title = "Average Marginal Effects of Unfollowing",
    subtitle = "Average marginal effects (no interactions) and 95% CIs of a +1\nSD change on probability of unfollowing",
    x = "Marginal Effect\n(Probability Scale)",
    y = "Coefficient"
  )
ggsave(
  "graph_overall.png",
  graph.overall,
  height = 5,
  width = 9,
  dpi = 300
) 

```

# Allfits
```{r}
mod <- readRDS("reaminimalsimpleY_bayes_rfx.rds")
a <- allFit(mod)
s
```


